Attestable Expiration with Trusted Platform Modules

### 2016-05-18 paper.tex
merged phils changes back in

Today, we have more choices than ever when it comes to deciding who can hold on to our sensitive data, and it is difficult to know who we can trust. Even though we may trust a party at a given time, it is impossible to know who might be compromised or subpeonaed in the future. In recent years, there have been an increasing number of cases where courts mandated that a third party hand over its encryption keys~\cite{hushmail}, and there has been increasing pressure from law enforcement for services to incorporate a government ``back-door''~\cite{backdoor}. Also, data is copied so cheaply and freely that even if we explicitly delete some piece of data through an application's API, there is no mechanism in place to ensure us that \textit{all} copies have been deleted, or that it has not been shared with some other party.

These situations could be mitigated by the existence of a system in which sensitive data expired after a given time. In this paper, we attempt to provide one possible realization of such a system. The difficulty in implementing expiring information lies in the difficulty of proving a negative. Namely, whoever is holding on to the sensitive data must prove not only that they deleted the data, but also that they didn't make a copy of it beforehand. In order to achieve this property, we leverage two areas of prior work on cryptographic proofs-of-work: Trusted Platform Modules (TPMs), and Ethereum smart contracts. TPMs allow one to ensure that code has been executed correctly and without modification, and smart contracts allow for the creation of an incentive system that encourages and rewards good behavior.

>>>>

Today, we have more choices than ever when it comes to deciding who can hold on to our sensitive data, and it is difficult to know whom to trust. Even though we may trust a party at a given time, it is impossible to know who might be compromised or subpeonaed in the future. In recent years, there have been an increasing number of cases where courts mandated that a third party hand over its encryption keys~\cite{hushmail}, and there has been increasing pressure from law enforcement for services to incorporate a government ``back-door''~\cite{backdoor}. Also, data is copied so cheaply and freely that even if we explicitly delete some piece of data through an application's API, there is no mechanism in place to ensure us that \textit{all} copies have been deleted, or that none of them have not been shared with some other party.

These situations could be mitigated by the existence of a system in which sensitive data expired after a given time. In this paper, we attempt to provide one possible realization of such a system. The difficulty in implementing expiring information lies in the difficulty of proving a negative. Namely, whoever is holding on to the sensitive data must prove not only that they deleted the data, but also that they didn't make a copy of it beforehand. In order to achieve this property, we leverage two areas of prior work: Trusted Platform Modules (TPMs), and Ethereum smart contracts. TPMs allow one to provably attest that a given piece of code has been executed without modification, along with its inputs and outputs, and smart contracts allow for the creation of an incentive system that encourages and rewards good behavior.
